### 2025-03-21 tesis_David_Lic/Chapter4/chapter4.tex
tesis final

%https://indico.cern.ch/event/1244981/contributions/5230942/attachments/2581191/4452030/POG_pres.pdf
\item Residual beam positions. To investigate additional deviations of the beams, a fit model is created by combining the nominal beam positions, the orbit drift correction, and the beam-beam deflection. In order to accommodate the unknown response of the Beam Position Monitors (BPM) to the beam-beam deflection, the beam-beam deflection is scaled using a parameter that is allowed to freely vary \cite{lumi_precise_2015_2016}. Moreover, length scale factors are also included as freely floating parameters.

In general, the residual deviations are less than 2 $\mum$. The primary source of uncertainty here is from the scale of the beam-beam deflection. Varying the scale parameter within the range of values found by the fit results in a change of $\sigma_{vis}$ of up to 1.0\%. This value is assigned as an uncertainty.\\

@@

Taking into account the above considerations, the total systematic uncertainty is found to be 0.73\% ($30.3 \text{ mb}$).
\newpage
\begin{table}[!ht]
\centering
\caption[Systematic Uncertainties]{Total systematic uncertainties for the calibration.}
\label{systematics}
\begin{tabular}{lc}
                               & \multicolumn{1}{l}{}       \\
                               & \multicolumn{1}{l}{}       \\
            & \textbf{Systematic Uncertainty [\%]}  \\ 
\toprule
Length scale                   & 0.12                        \\
Orbit drift                    & 0.3                        \\
%Residual beam positions & 1.0                \\
%Factorization bias & 1.4                        \\
Beam-beam effects              & 0.5                        \\
Beam current calibration       & 0.2                        \\
Ghost and satellite            & 0.1                        \\
Scan to scan variation         & 0.26                        \\
Bunch to bunch variation       & 0.1                        \\
%Cross detector consistency     & -                          \\
Background subtraction         & 0.24                          \\ 
\hline
\textbf{Total}                 & \textbf{0.73}               
\end{tabular}
\end{table}

>>>>

%https://indico.cern.ch/event/1244981/contributions/5230942/attachments/2581191/4452030/POG_pres.pdf
%\item Residual beam positions. To investigate additional deviations of the beams, a fit model is created by combining the nominal beam positions, the orbit drift correction, and the beam-beam deflection. In order to accommodate the unknown response of the Beam Position Monitors (BPM) to the beam-beam deflection, the beam-beam deflection is scaled using a parameter that is allowed to freely vary \cite{lumi_precise_2015_2016}. Moreover, length scale factors are also included as freely floating parameters.

%In general, the residual deviations are less than 2 $\mum$. The primary source of uncertainty here is from the scale of the beam-beam deflection. Varying the scale parameter within the range of values found by the fit results in a change of $\sigma_{vis}$ of up to 1.0\%. This value is assigned as an uncertainty.\\

@@

Taking into account the above considerations, the total systematic uncertainty is found to be 0.73\% ($30.3 \text{ mb}$).
%\newpage
\begin{table}[!ht]
\centering
\caption[Systematic Uncertainties]{Total systematic uncertainties for the calibration.}
\label{systematics}
\begin{tabular}{lc}
                               & \multicolumn{1}{l}{}       \\
                               & \multicolumn{1}{l}{}       \\
            & \textbf{Systematic Uncertainty [\%]}  \\ 
\toprule
Length scale                   & 0.12                        \\
Orbit drift                    & 0.3                        \\
%Residual beam positions & 1.0                \\
%Factorization bias & 1.4                        \\
Beam-beam effects              & 0.5                        \\
Beam current calibration       & 0.2                        \\
Ghost and satellite            & 0.1                        \\
Scan to scan variation         & 0.26                        \\
Bunch to bunch variation       & 0.1                        \\
%Cross detector consistency     & -                          \\
Background subtraction         & 0.24                          \\ 
\hline
\textbf{Total}                 & \textbf{0.73}               
\end{tabular}
\end{table}

### 2025-03-21 tesis_David_Lic/Portada/Portada.tex
tesis final

 %% Aquí comienza el documento.
\thispagestyle{empty} %% PARA QUITAR FORMATO DE PIES Y ENCABEZADOS DE PÁGINA A LA PORTADA
%
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%% MINIPAGE PARA EL LOGO DEL LADO IZQUIERDO (UNIVERSIDAD) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%
%\fbox{
\begin{minipage}[c][0.15\textheight][c]{0.25\textwidth}
    \begin{center}
        \includegraphics[height=3.2cm, keepaspectratio=true]{unison-logo.png} %% LOGO IZQUIERDO
    \end{center}
\end{minipage}
%}
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%%%%%% MINIPAGE PARA EL CUERPO DE LA PORTADA (NOMBRES, TITULOS, ETC.) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%
%
%
%
%\fbox{
\begin{minipage}[c][0.17\textheight][t]{0.7\textwidth}
    \begin{center}
        {\scshape\LARGE UNIVERSIDAD DE SONORA} %% NOMBRE DE LA UNIVERSIDAD
        \vspace{.5cm}   %% DEFINE EL ESPACIO ENTRE EL NOMBRE DE LA UNIVERSIDAD Y LA LÍNEA DOBLE
        \hrule height2.5pt  %% DEFINE EL ANCHO DE LA PRIMER LÍNEA
        \vspace{.1cm}    %% DEFINE EL ESPACIO ENTRE LAS DOS LINEAS
        \hrule height1pt  %% DEFINE EL ANCHO DE LA SEGUNDA LINEA (NORMALMENTE ES MAS DELGADA)
        \vspace{.4cm}   %% DEFINE EL ESPACIO ENTRE LA DOBLE LINEA Y EL NOMBRE DE LA DIVISIÓN
        {\scshape \large Facultad Interdisciplinaria de Ciencias Exactas y Naturales}
        {\scshape Departamento de Investigaci\'on en F\'isica} %% NOMBRE DE LA DIVISIÓN
    \end{center}
\end{minipage}
%}
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%% MINIPAGE PARA EL LOGO DEL LADO DERECHO (DIVISIÓN ACADÉMICA)
%
%
%
%
%\fbox{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%
%
%  ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%
%%%%%%%%%%%%%%%% 5TO MINIPAGE PARA EL CUERPO DE LA PORTADA (NOMBRES, TÍTULO, ETC.) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%
%\fbox{
\begin{minipage}[l][0.78\textheight][t]{0.1\textwidth}
    \begin{center}
    \hskip0pt
    \vrule width2.5pt height17cm    %% height definde la altura de la linea gruesa
        \hskip1mm
        \vrule width1pt height17cm  %% height define la altura de la linea delgada
        \end{center}
\end{minipage}
%}
%\fbox{
\begin{minipage}[c][0.78\textheight][t]{0.8\textwidth}
      \begin{center}
      \vspace{2cm}
        {\Large \scshape {Desarrollo y calibración del sistema de medición de luminosidad del detector de píxeles de silicio CMS}}

@@

        \makebox[5cm][c]{\LARGE Monograf\'ia}  \\[20pt]
         En cumplimiento parcial de los requisitos para el grado de:\\[5pt]
        {\Large \textbf{{Doctorado en Ciencias (F\'isica)}}}\\[40pt]
        By:\\[12pt]
        \textbf{  {\large Luis Enriquue Enrique CUEVAS PICOS}}

@@

        { \large Director}:\\Dr. Jose Feliciano BENITEZ RUBIO

@@

        { Hermosillo, Sonora} \hskip2.5cm { - - -, 2025}
      \end{center}
\end{minipage}
%}

>>>>

 %% Aquí comienza el documento.
\thispagestyle{empty} %% PARA QUITAR FORMATO DE PIES Y ENCABEZADOS DE PÁGINA A LA PORTADA
%
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%% MINIPAGE PARA EL LOGO DEL LADO IZQUIERDO (UNIVERSIDAD) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%
%\fbox{
\begin{minipage}[c][0.15\textheight][c]{0.25\textwidth}
    \begin{center}
        \includegraphics[height=3.2cm, keepaspectratio=true]{unison-logo.png} %% LOGO IZQUIERDO
    \end{center}
\end{minipage}
%}
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%%%%%% MINIPAGE PARA EL CUERPO DE LA PORTADA (NOMBRES, TITULOS, ETC.) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%
%
%
%
%\fbox{
\begin{minipage}[c][0.17\textheight][t]{0.7\textwidth}
    \begin{center}
        {\scshape\LARGE UNIVERSIDAD DE SONORA} %% NOMBRE DE LA UNIVERSIDAD
        \vspace{.5cm}   %% DEFINE EL ESPACIO ENTRE EL NOMBRE DE LA UNIVERSIDAD Y LA LÍNEA DOBLE
        \hrule height2.5pt  %% DEFINE EL ANCHO DE LA PRIMER LÍNEA
        \vspace{.1cm}    %% DEFINE EL ESPACIO ENTRE LAS DOS LINEAS
        \hrule height1pt  %% DEFINE EL ANCHO DE LA SEGUNDA LINEA (NORMALMENTE ES MAS DELGADA)
        \vspace{.4cm}   %% DEFINE EL ESPACIO ENTRE LA DOBLE LINEA Y EL NOMBRE DE LA DIVISIÓN
        {\scshape \large Facultad Interdisciplinaria de Ciencias Exactas y Naturales}\\
        {\scshape Departamento de F\'isica} %% NOMBRE DE LA DIVISIÓN
    \end{center}
\end{minipage}
%}
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%% MINIPAGE PARA EL LOGO DEL LADO DERECHO (DIVISIÓN ACADÉMICA)
%
%
%
%
%\fbox{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%
%
%  ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%
%%%%%%%%%%%%%%%% 5TO MINIPAGE PARA EL CUERPO DE LA PORTADA (NOMBRES, TÍTULO, ETC.) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%
%\fbox{
\begin{minipage}[l][0.78\textheight][t]{0.1\textwidth}
    \begin{center}
    \hskip0pt
    \vrule width2.5pt height17cm    %% height definde la altura de la linea gruesa
        \hskip1mm
        \vrule width1pt height17cm  %% height define la altura de la linea delgada
        \end{center}
\end{minipage}
%}
%\fbox{
\begin{minipage}[c][0.78\textheight][t]{0.8\textwidth}
      \begin{center}
      \vspace{2cm}
        {\Large \scshape {Estudio del modelo de ruido para la medici\'on de luminosidad con Pixel Cluster Counting en CMS}}

@@

        \makebox[5cm][c]{\LARGE TESIS}  \\[20pt]
         en cumplimiento parcial para conseguir el grado de:\\[5pt]
        {\Large \textbf{{LICENCIADO EN FISICA}}}\\[40pt]
        Por:\\[12pt]
        \textbf{  {\large David Alonso Guzm\'an L\'opez}}

@@

        { \large Director}:\\Dr. Jose Feliciano Benitez Rubio

@@

        { Hermosillo, Sonora} \hskip2.5cm {2025}
      \end{center}
\end{minipage}
%}

### 2025-03-21 tesis_David_Lic/chap_originales/Chapter2/chapter2.tex
tesis final

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=.3]{Chapter2/slice_det.png}
    \caption[Transverse slice view of the CMS detector]{Transverse slice of the CMS detector with some particle interactions (from the beam interaction region to the muon detector) \cite{det_summary}.}
    \label{slice_CMS}
  \end{figure}
\end{center}

@@

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=.3]{Chapter2/detectors.png}
    \caption[Layout of the luminometers in the CMS detector]{The seven luminometers that make up the CMS luminosity measurement system. Multiple independent systems used online: BCM1F, HFET, HFOC, PLT (independently calibrated) ,REMUS and  DT (cross-calibrated) , Pixel cluster counting is used after offline processing.}
    \label{luminometers}
  \end{figure}
\end{center}

@@

\begin{center}
  \begin{figure}[h]
    \centering
    \includegraphics[scale=.2]{Chapter2/modules_drawing.png}
    \caption[Types of modules in the pixel detector]{ Drawings of the pixel detector modules for BPIX L1 (left), BPIX L2–4 (middle), and the FPIX detector (right)\cite{phase1_Pixel_Detector}.}
    \label{modules_drawing}
  \end{figure}
\end{center}

\begin{center}
  \begin{figure}[h]
    \centering
    \includegraphics[scale=.3]{Chapter2/PixelSensor.png} \includegraphics[scale=.3]{Chapter2/hit.png}
    \caption[Schematic view of a pixel sensor and its connection to the readout channels]{ left: layout pixel sensor conected to a readout chip , right: hits detection in a corresponding  pixel sensor \citep{thomson_2013}. }
    \label{module and hit}
  \end{figure}
\end{center}

@@

Figure \ref{cluster}  shown an example of how a pixel cluster is constructed. Each square in the figure represents a pixel. The red pixels indicate that they have the required charge up to 2000 electrons to be considered valid pixels and are therefore included in the cluster. On the other hand, the green pixels correspond to charge depositions below the 2000 electron threshold and are not included in the cluster.
The dotted blue line in the figure represents the trajectory of the particle traveling parallel to the x-z plane. As it travels, it activates pixels in its path precisely, as well as pixels that are deviated from its trajectory due to the Lorentz drift \cite{Pixel_Hit_Reconstruction}.\\
\newpage
\begin{center}
  \begin{figure}[h]
    \centering
    \includegraphics[scale=.25]{Chapter2/pixel_cluster.png} 
    \caption[Construction of a pixel cluster]{ The figure illustrates a pixel cluster example with a total charge up of 4,000 electrons, required to be a valid cluster. The red pixels have the required charge while the green one does not.}
    \label{cluster}
  \end{figure}
\end{center}

>>>>

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=.3]{Chapter2/slice_det.png}
    \caption[Transverse slice fo CMS detector]{Transverse slice of the CMS detector with some particle interactions (from the beam interaction region to the muon detector) \cite{det_summary}.}
    \label{slice_CMS}
  \end{figure}
\end{center}

@@

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=.3]{Chapter2/detectors.png}
    \caption[CMS Luminometers]{The seven luminometers that make up the CMS luminosity measurement system. Multiple independent systems used online: BCM1F, HFET, HFOC, PLT (independently calibrated) ,REMUS and  DT (cross-calibrated) , Pixel cluster counting is used after offline processing.}
    \label{luminometers}
  \end{figure}
\end{center}

@@

\begin{center}
  \begin{figure}[h]
    \centering
    \includegraphics[scale=.2]{Chapter2/modules_drawing.png}
    \caption[Pixel detector modules]{ Drawings of the pixel detector modules for BPIX L1 (left), BPIX L2–4 (middle), and the FPIX detector (right)\cite{phase1_Pixel_Detector}.}
    \label{modules_drawing}
  \end{figure}
\end{center}

\begin{center}
  \begin{figure}[h]
    \centering
    \includegraphics[scale=.3]{Chapter2/PixelSensor.png} \includegraphics[scale=.3]{Chapter2/hit.png}
    \caption[PixelSensor]{ left: layout pixel sensor conected to a readout chip , right: hits detection in a corresponding  pixel sensor \citep{thomson_2013}. }
    \label{module and hit}
  \end{figure}
\end{center}

@@

Figure \ref{cluster}  shown an example of how a pixel cluster is constructed. Each square in the figure represents a pixel. The red pixels indicate that they have the required charge up to 2000 electrons to be considered valid pixels and are therefore included in the cluster. On the other hand, the green pixels correspond to charge depositions below the 2000 electron threshold and are not included in the cluster.
The dotted blue line in the figure represents the trajectory of the particle traveling parallel to the x-z plane. As it travels, it activates pixels in its path precisely, as well as pixels that are deviated from its trajectory due to the Lorentz drift \cite{Pixel_Hit_Reconstruction}.\\
\newpage
\begin{center}
  \begin{figure}[h]
    \centering
    \includegraphics[scale=.25]{Chapter2/pixel_cluster.png} 
    \caption[Pixel cluster]{ The figure illustrates a pixel cluster example with a total charge up of 4,000 electrons, required to be a valid cluster. The red pixels have the required charge while the green one does not.}
    \label{cluster}
  \end{figure}
\end{center}
